---
title: "Homework 1"
author: "Katie Schaper"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## C=0
```{r c}
source('~/Desktop/qscript.R')
x <- seq(from=-10, to=10, by=.5)
y <- quad(x,a=1,b=1)
plot(x,y)
```
First we tested quadratics with C=0. 
This produced the graph shown.

## B=0
```{r b}
source('~/Desktop/qscript.R')
x <- seq(from=-10, to=10, by=.5)
y <- quad(x,a=1,c=1)
plot(x,y)
```
Next we tested quadratics with B=0. 
This graph varied slightly from the previous one.

## A=0
```{r a}
source('~/Desktop/qscript.R')
x <- seq(from=-10, to=10, by=.5)
y <- quad(x,b=1,c=1)
plot(x,y)
```
Then we tested quadratics with A=0. 
This produced a linear graph with a slope of 1 and a y intercept of 1.

## A=0,B=0
```{r ab}
source('~/Desktop/qscript.R')
x <- seq(from=-10, to=10, by=.5)
y <- quad(x,c=1)
plot(x,y)
```
We tested A=0 and B=0. 
This produced a horizontal line with a y intercept of 1.

## A=0,C=0
```{r ac}
source('~/Desktop/qscript.R')
x <- seq(from=-10, to=10, by=.5)
y <- quad(x,b=1)
plot(x,y)
```
Then we tested A=0 and C=0. 
This produced a linear graph with a slope of 1 and an intercept at y=0, x=0.

## B=0,C=0
```{r bc}
source('~/Desktop/qscript.R')
x <- seq(from=-10, to=10, by=.5)
y <- quad(x,a=1)
plot(x,y)
```
Finally we tested quadratics with B=0 and C=0. 
This produced a quadratic graph with its base at y=0, x=0.
